Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-15 paper-ieee-trans.tex
Add a reference to SQA baseline document

The SQA criteria are a set of conventions and recommendations that pave the way for
the adequate development, timely deliver and reliable operation of the produced software components.
It emphasizes the quality requirements and best practices to be applied at the
development phase, such as style and testing compliance or human code reviews, to protect the
production source code versions. Furthermore, the criteria promote the adoption of the software
by providing minimum requirements of documentation content and stressing the usage of automated
solutions for software deployment.

@@

>>>>

The SQA criteria are a set of conventions and recommendations that pave the way for
the adequate development, timely delivery and reliable operation of the produced software components.
It emphasizes the quality requirements and best practices to be applied at the
development phase, such as style and testing compliance or human code reviews, to protect the
production source code versions. Furthermore, the criteria promote the adoption of the software
by providing minimum requirements of documentation content and stressing the usage of automated
solutions for software deployment. The SQA criteria is continuously evolving \cite{sqa-baseline}, aiming at serving
as a reference for future software development projects within the European research ecosystem.

@@

\bibitem{sqa-baseline}
Pablo Orviz et al.,
A set of common software quality assurance baseline criteria for research projects,
2017.
[Online] Available: \url{http://digital.csic.es/bitstream/10261/160086/4/CommonSQA-v2.pdf}
